---
title: "Homework 5"
author: "Beibei Cao"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

Read in the data.

```{r}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```


Let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved), 
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

Try to iterate ........

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```



```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```



```{r, error = TRUE}
city_prop_test = function(df) {
  
  n_unsovled ...
  n_total ... 
  
  prop.test(.....)
  
}
homicide_df = 
  read_csv("homicide_data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved",
    )
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") %>% 
  nest(data = resolved)
```


## Problem 2

Import and tidy the data from each file.
```{r, error = TRUE}
study_df = 
  # get file paths
  tibble(
    path = list.files("lda_data"),
  ) %>%
  # read each file 
  mutate(
    subject = str_remove(path, '.csv'),
    path = str_c("lda_data/", path),
    data = map(.x = path, ~read_csv(.x))
    ) %>% 
  # tidy data
  separate(subject, c("arm", "id"), remove = FALSE) %>% 
  mutate(
    arm = recode(arm, con = "control", exp = "experimental"),
    id = as.integer(id)
         ) %>%
  unnest(data) %>% 
  select(-path)
```

Make a spaghetti plot showing observations on each subject over time.

```{r fig.width = 10, fig.height = 6}
study_df %>% 
  # transform into long format 
  pivot_longer(
    week_1:week_8,
    names_prefix = "week_",
    names_to = "week",
    values_to = "observation"
  ) %>% 
  # plot 
  ggplot(aes(x = week, y = observation, group = interaction(arm, id), color = arm)) +
  geom_point() + geom_line() +
  labs(
    title = "Observations over Time",
    x = "Week",
    y = "Observation",
    color = "Arm"
  )
```

It could be observed from the plot that the experimental group subjects generally have higher observations than the control group. There is also an increasing trend in the observations of the experimental group while the observations in the control group are stable across the 8 weeks.

# Problem 3

